Tesseroids: command-line tools for gravity field forward modeling in spherical coordinates

### 2014-04-01 manuscript.tex
Started implementation section

@@

\citet{Barrera-Figueroa2006}.

>>>>

Data and source code to produce the results of this comparison
are provided by \textbf{(cite notebook on figshare)}.

@@

The methods described above
were implemented the software package
Tesseroids version 1.1.1.
The package consists
of a range of command-line programs
written in the C programming language.
Tesseroids is free and open-source software
under the terms of
the 3-clause BSD license.

Each program performs a single type of calculation.
Programs receive input from
the standard input stream (\texttt{stdin})
and command-line arguments.
Output is made in plain text
through the standard output stream (\texttt{stdout}).

The main programs in Tesseroids are
\texttt{tesspot},
\texttt{tessgx},
\texttt{tessgy},
\texttt{tessgz},
\texttt{tessgxx},
\ldots ,
\texttt{tessgzz}
(henceforth referred to collectively as \texttt{tess*} programs).
These programs
calculate the gravitational potential,
gravitational attraction,
and Marussi tensor
caused by a tesseroid model.
The computation points are passed
through the standard input stream
and the tesseroid model
is passed through
a simple model file.
All programs receive
optional command-line arguments
that control the GLQ order (default is $N^\lambda=N^\phi=N^r=2$)
and distance/size ratio $R$
for the recursive division scheme.

The complete list of programs provided in Tesseroids is:

\begin{itemize}
    \item \texttt{tesspot}, \texttt{tessgx}, \texttt{tessgy}, \texttt{tessgz},
        \texttt{tessgxx}, \texttt{tessgxy}, \texttt{tessgxz},
        \texttt{tessgyy}, \texttt{tessgyz}, \texttt{tessgzz}:
        Calculate the gravitational potential, gravitational attraction,
        and Marussi tensor caused by a tesseroid model.
    \item \texttt{prismpot},
        \texttt{prismgx}, \texttt{prismgy}, \texttt{prismgz},
        \texttt{prismgxx}, \texttt{prismgxy}, \texttt{prismgxz},
        \texttt{prismgyy}, \texttt{prismgyz}, \texttt{prismgzz}:
        Calculate the gravitational potential, gravitational attraction,
        and Marussi tensor caused by a right-rectangular prism model
        in Cartesian coordinates
        using the formula of \citet{Nagy2000}.
    \item \texttt{prismpots}, \texttt{prismgs}, \texttt{prismggts}:
        Calculate the gravitational potential, gravitational attraction,
        and Marussi tensor caused by a right-rectangular prism model
        in spherical coordinates
        using the formula of \citet{Wild-Pfeiffer2008}.
    \item \texttt{tess2prism}: Converts a tesseroid model into
        right-rectangular prisms of equal mass.
    \item \texttt{tessgrd}: Generate regular grids.
    \item \texttt{tessdefaults}: Output the default values
        and values of physical constants used.
    \item \texttt{tessmodgen}: Generate a tesseroid model
        from a gridded relief (e.g., a digital elevation model).
    \item \texttt{tesslayers}: Generate a tesseroid model of
        a series of stacked layers.
    \item \texttt{tessmass}: Calculate the total mass of a tesseroid model.
\end{itemize}

Tesseroids is freely available
online\footnote{www.leouieda.com/tesseroids}.
\textbf{(cite archive on figshare)} provides a persistent
archive for the source code and compiled binaries of Tesseroids.
